On finiteness of structures produced deterministically by oritatami co-transcriptional folding \thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~S.}

### 2018-11-09 uos_preliminaries.tex
Preliminaries almost done.
We should add anything, whenever the need arises.

An \textit{oritatami system} (OS) is a 6-tuple $\Xi = (\Sigma, R, \alpha, \delta, \sigma, w)$, where $\Sigma$ is a set of bead types, $R\subseteq \Sigma \times \Sigma$ is a rule set, $\alpha$ is an arity, $\delta \ge 1$ is a parameter called the \textit{delay}, $\sigma$ is an initial $R$-valid conformation of arity at most $\alpha$ over $\Sigma$ called the \textit{seed}, upon which its finite \textit{transcript} $w \in \Sigma^*$ is to be folded by stabilizing beads of $w$ one at a time so as to minimize energy collaboratively with the succeeding $\delta{-}1$ nascent beads. 
The energy of a conformation $C = (P, w, H)$, denoted by $\Delta G(C)$, is defined to be ${-}|H|$; the more bonds a conformation has, the more stable it gets. 
The set $\mathcal{F}(\Xi)$ of conformations \textit{foldable} by the system $\Xi$ is recursively defined as: the seed $\sigma$ is in $\mathcal{F}(\Xi)$; and provided that an elongation $C_i$ of $\sigma$ by the prefix $w[1..i]$ be foldable (i.e., $C_0 = \sigma$), its further elongation $C_{i+1}$ by the next bead $w[i+1]$ is foldable if 
\begin{equation}\label{eq:OS_CF}
C_{i+1} \in \argmin_{
\substack{
C \in \mathcal{C}_{\le \alpha} s.t. \\
C_i \xrightarrow{R}_{w[i+1]}C \\
}
}
\min \Bigl\{ \Delta G(C') \Bigm|
C \xrightarrow{R}^*_{w[i+2...i+k]}C', k\le \delta, C' \in \mathcal{C}_{\le \alpha}
\Bigr\}.
\end{equation}
%
Then we say that the bead $w[i+1]$ and the bonds it forms are \textit{stabilized} according to $C_{i+1}$. 
Note that an arity-$\alpha$ oritatami system cannot fold any conformation of arity larger than $\alpha$. 
A conformation foldable by $\Xi$ is \textit{terminal} if none of its elongations is foldable by $\Xi$. 
The OS $\Xi$ is \textit{deterministic} if for all $i \ge 0$, there exists at most one $C_{i+1}$ that satisfies \eqref{eq:OS_CF}. 
A deterministic oritatami system folds into a unique terminal conformation.

In this paper, we mainly consider the unary oritatami system. 
An oritatami system is \textit{unary} if its bead type set $\Sigma$ is of size 1. 
Its sole element is denoted by $a$, that is, $\Sigma = \{a\}$. 
Its only possible rule is $(a, a)$ and without that, the system would not fold into anything meaningful but just into any elongation of its seed nondeterministically.

>>>>

An \textit{oritatami system} (OS) is a 6-tuple $\Xi = (\Sigma, R, \alpha, \delta, \sigma, w)$, where $\Sigma$ is a set of bead types, $R\subseteq \Sigma \times \Sigma$ is a rule set, $\alpha$ is an arity, $\delta \ge 1$ is a parameter called the \textit{delay}, $\sigma$ is an initial $R$-valid conformation of arity at most $\alpha$ over $\Sigma$ called the \textit{seed}, upon which its finite \textit{transcript} $w \in \Sigma^*$ is to be folded by stabilizing beads of $w$ one at a time so as to minimize energy collaboratively with the succeeding $\delta{-}1$ nascent beads. 
The energy of a conformation $C = (P, w, H)$, denoted by $\Delta G(C)$, is defined to be ${-}|H|$; the more bonds a conformation has, the more stable it gets. 
The set $\mathcal{F}(\Xi)$ of conformations \textit{foldable} by the system $\Xi$ is recursively defined as: the seed $\sigma$ is in $\mathcal{F}(\Xi)$; and provided that an elongation $C_i$ of $\sigma$ by the prefix $w[1..i]$ be foldable (i.e., $C_0 = \sigma$), its further elongation $C_{i+1}$ by the next bead $w[i+1]$ is foldable if 
\begin{equation}\label{eq:OS_CF}
C_{i+1} \in \argmin_{
\substack{
C \in \mathcal{C}_{\le \alpha} s.t. \\
C_i \xrightarrow{R}_{w[i+1]}C \\
}
}
\min \Bigl\{ \Delta G(C') \Bigm|
C \xrightarrow{R}^*_{w[i+2...i+k]}C', k\le \delta, C' \in \mathcal{C}_{\le \alpha}
\Bigr\}.
\end{equation}
%
Then we say that the bead $w[i+1]$ and the bonds it forms are \textit{stabilized} according to $C_{i+1}$. 
Note that an arity-$\alpha$ oritatami system cannot fold any conformation of arity larger than $\alpha$. 
A conformation foldable by $\Xi$ is \textit{terminal} if none of its elongations is foldable by $\Xi$. 
The OS $\Xi$ is \textit{deterministic} if for all $i \ge 0$, there exists at most one $C_{i+1}$ that satisfies \eqref{eq:OS_CF}. 
A deterministic oritatami system folds into a unique terminal conformation. 
An oritatami system with the empty rule set just folds into an arbitrary elongation of its seed nondeterministically. 
Thus, the rule set is always assumed to be non-empty.

In this paper, we mainly consider the unary oritatami system. 
An oritatami system is \textit{unary} if its bead type set $\Sigma$ is of size 1. 
Its sole bead type is denoted by $a$, that is, $\Sigma = \{a\}$. 
Its only possible rule is $(a, a)$ so that the non-empty rule set assumption implies that its rule set is $R = \{(a, a)\}$. 
Its transcript is a sequence of $a$-beads. 
That is to say, the behavior of a unary oritatami system is fully determined by the delay, arity, and seed.
